\label{chap:conclusion}

\section{Summary of Key Findings}
This thesis investigated the conflict between international price discrimination and consumer-driven geo-arbitrage.
\begin{itemize}
    \item \textbf{RQ1 (Incentive):} The Digital Services Price Index (DSPI) confirmed significant deviations from Purchasing Power Parity, creating massive economic incentives (often >70\% discounts) for consumers to engage in geo-arbitrage.
    \item \textbf{RQ2 (Response):} Strategies are determined by \textbf{Business Model}, not just price variance. The "Content Sector" has standardized on a high-intensity "Fortress Strategy" ($R \approx 0$) where strict enforcement is a baseline requirement for licensing, regardless of specific price gaps. In contrast, utility software relies on "Hard" cryptographic keys (Adobe) or compliance baselines (Microsoft), while VPN providers naturally exhibit minimal blocking enforcement, confirming an adversarial market structure.
    \item \textbf{Effectiveness:} While firms have increased the technical sophistication of their barriers (evidenced by the sharp uptake in \textbf{Technical Blocking} clauses from 2022 onwards), the persistence of "User Workaround" discussions suggests that enforcement creates friction but does not eliminate the practice.
\end{itemize}

\section{Contribution to Research}
The study contributes a standardized metric (DSPI) for measuring digital price dispersion and demonstrates the utility of Large Language Models (Gemini 3 Flash) in automating the analysis of complex legal-strategic texts. Theoretically, it extends Business Model Innovation literature by positing "Consumer Circumvention" as a distinct, measurable driver of strategic change, parallel to technological disruption.

\section{Future Outlook}
As regulatory frameworks like the EU's Digital Single Market evolve, the legality of geo-blocking will face further challenges. Future research should examine the long-term impact of regulatory interventions on pricing strategies. Ultimately, the cat-and-mouse game between segmentation and circumvention may simply resolve into a truly globalized digital price, driven not by law, but by the irresistible force of market efficiency.
