%%
%\documentclass{}[
	%english,
	%ruledheaders=section,           %Ebene bis zu der die Überschriften mit Linien abgetrennt werden, vgl. DEMO-TUDaPub
	%class=report ,                   % Basisdokumentenklasse. Wählt die Korrespondierende KOMA-Script Klasse
	%thesis={type=bachelor},         % Dokumententyp Thesis, für Dissertationen siehe die Demo-Datei DEMO-TUDaPhd
	%accentcolor=9c,% Auswahl der Akzentfarbe
	%custommargins=true,% Ränder werden mithilfe von typearea automatisch berechnet
	%marginpar=false,% Kopfzeile und Fußzeile erstrecken sich nicht über die Randnotizspalte
	%BCOR=5mm,%Bindekorrektur, falls notwendig
	%parskip=half-,%Absatzkennzeichnung durch Abstand vgl. KOMA-Script
	%fontsize=11pt,%Basisschriftgröße laut Corporate Design ist mit 9pt häufig zu klein
	%logofile={figures/tuda_logo.pdf},
    %pdfa=false
%]%{tudapub}

\documentclass[
	english,
	ruledheaders=section,
	class=report,
	thesis={type=master},
	accentcolor=9c,
	custommargins=geometry,%CHANGED FROM TRUE TO FALSE
	marginpar=false,
	parskip=half-,
	fontsize=12pt,
	logofile={figures/tuda_logo.pdf},
    pdfa=true
]{tudapub}

%\usepackage{showframe}
%\usepackage[reset, left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm, includefoot]{geometry}
%\geometry{a4paper, left=2.5cm, right=2.5cm, top=2.5cm, bottom=2.5cm, includefoot}
\geometry{reset, bottom=2.5cm, includefoot} 


\usepackage[main=english, ngerman]{babel}
\usepackage[autostyle]{csquotes}
\usepackage{microtype}

\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{threeparttable}
\renewcommand{\TPTnoteSettings}{\fontsize{10}{12}\selectfont} %<-- Add this line
\usepackage{pifont}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,positioning,calc}

\usepackage{setspace}
\onehalfspacing

% Use KOMA-Script recommended method for section formatting
\RedeclareSectionCommand[
    beforeskip=0pt,
    afterskip=10pt
]{chapter}


% Ensure titlesec is not loaded (remove any \usepackage{titlesec} lines)
\usepackage{caption}
\DeclareCaptionFont{tenpoint}{\fontsize{10}{12}\selectfont}
\captionsetup{font=tenpoint}


%change the apa6 to apa when you want to use the APA 7th edition
\usepackage[backend=biber, style=apa, sorting=nyt]{biblatex}
\addbibresource{Bibliography.bib}

\usepackage[acronym, section]{glossaries}
%%\newacronym[plural=JOLs]{jol}{JOL}{Judgement of Learning}
%\newacronym[plural=JOLs, longplural={Judgements of Learning}]{jol}{JOL}{Judgement of Learning}
%\newacronym[plural=MJs]{mj}{MJ}{Memorability Judgement}
%\newacronym{ore}{ORE}{Other-Race Effect}
%%\newacronym{ffa}{FFA}{Fusiform Face Area}
%\newacronym{fmri}{fMRI}{Functional Magnetic Resonance Imaging}





\makeglossaries

% change count of figures and tables to not include chapter number
\usepackage{chngcntr}
\counterwithout{figure}{chapter}
\counterwithout{table}{chapter}

%\newglossaryentry{realschulabschluss}{
%    name={Realschulabschluss},
%    description={A German secondary school certificate, approximately equivalent to a high school diploma or GCSEs.}
%}



\title{Business Model Responses to Consumer Circumvention: Lessons from Piracy Applied to VPN-Enabled Geo-Arbitrage}
\author{Tim Weckbach}
\reviewer{William Schütte \and Prof. Dr. Alexander Kock}









\begin{document}

%\setlength{\textheight}{24cm}
%\setlength{\topmargin}{-1.2cm} % Muss oft angepasst werden
%\setlength{\headsep}{1cm}
%\setlength{\footskip}{1.5cm}
%\setlength{\voffset}{5cm}


\Metadata{
    \title{Business Model Responses to Consumer Circumvention: Lessons from Piracy Applied to VPN-Enabled Geo-Arbitrage}
    \author[Tim Weckbach]{Tim Weckbach}
    \keywords{Price Discrimination, Geo-Arbitrage, Business Model Innovation, VPN, Digital Services Price Index}
    \publisher{TU Darmstadt}
    \copyright{Tim Weckbach}
    \birthplace{Frankfurt am Main}
    \reviewer{William Schütte \and Prof. Dr. Alexander Kock}
}
\department{Business Informatics} 
\institute{Technology and Innovation Management}
\submissiondate{27.02.2026}
\maketitle

\begin{abstract}
This document outlines the structure for a thesis investigating business model responses to VPN-enabled geo-arbitrage. It begins by defining the core problem and research path. The study employs a mixed-methods approach to first quantify international price differentiation for digital services via a "Digital Services Price Index" (DSPI) and then qualitatively analyze the strategic responses of both digital service providers and VPN providers. The research draws parallels between modern geo-arbitrage and historical digital piracy to understand the pressures on existing business models and the drivers for innovation.

\end{abstract}

\noindent\textbf{Keywords:} Price Discrimination, Geo-Arbitrage, Business Model Innovation, VPN, Digital Services Price Index
\tableofcontents


\chapter{Introduction}
\input{introduction}

\chapter{Theoretical Foundations \& Literature Review}
\input{theory_background}

\chapter{Research Methodology}
\input{methodology}

\chapter{Results}
\input{results}

\chapter{Discussion}
\input{discussion}

\chapter{Conclusion}
\input{conclusion}





\backmatter
    \addcontentsline{toc}{chapter}{Bibliography}
    \printbibliography

    %--- List of Figures and Tables ---
    \cleardoublepage
    \phantomsection
    \addcontentsline{toc}{chapter}{List of Figures and Tables}
    \chapter*{List of Figures and Tables}
    \makeatletter
        \section*{\listfigurename} 
        \@starttoc{lof} 
        \vspace{1em} 
        \section*{\listtablename}
        \@starttoc{lot} 
    \makeatother

    %--- Glossary and Acronyms ---
    \cleardoublepage
    \phantomsection
    \addcontentsline{toc}{chapter}{Glossary and Acronyms}
    \chapter*{Glossary and Acronyms}
    \printglossaries

    \affidavit


\end{document}
