This chapter details how the research will be conducted.
\label{chap:methodology}

To measure the concepts of 'Coercion' and 'Technical Barriers', we used the 'Litigious' and 'Constraining' word lists from Loughran and McDonald (2011). These are the standard for finding legal risk in financial texts.

\section{Research Design}

This study adopts a sequential explanatory mixed-methods design, combining quantitative price analysis with qualitative text classification. The rationale for this dual approach is to first establish the \textit{magnitude} of the economic phenomenon (the arbitrage incentive) and then investigate the \textit{strategic responses} of the actors involved (firms and consumers). 

The quantitative phase (Phase 1) constructs the "Digital Services Price Index" (DSPI) to objectively measure the variance in global digital pricing. The qualitative phase (Phase 2) leverages a Large Language Model (LLM) pipeline to classify corporate disclosures and Terms of Service, mapping the strategic "frames" firms use to legitimize or combat this variance. This integration allows for a holistic understanding of the geo-arbitrage ecosystem.

\section{Phase 1: Quantitative Data Collection (for RQ1)}

\subsection{Data Collection}
To construct the DSPI, a representative basket of digital services was selected, covering three primary categories: Video on Demand (e.g., Netflix, Disney+), Music Streaming (e.g., Spotify, Apple Music), and Software/Gaming (e.g., Microsoft 365, Steam).

Price data was collected from a broad sample of over 30 countries to capture the full spectrum of purchasing power. From this dataset, a core sub-sample of key markets was selected for detailed "Affordability" analysis, including: Argentina, Australia, Brazil, Canada, France, Germany, India, Italy, Japan, Mexico, Netherlands, Poland, Spain, Switzerland, Turkey, Ukraine, United Kingdom, and the United States. Only countries with high-confidence official wage data were included.

Data collection was performed using a \textbf{Digital Audit} design, adapting the methodology established by \textcite{hannak2014measuring} for detecting online price discrimination. A virtual presence was established in each target country using a commercial VPN to simulate local access, a technique now standard in information systems research for "mystery shopping" in digital markets. For each service and country, the "Standard" monthly subscription price was recorded in the local currency. This approach mirrors the "Billion Prices Project" methodology \parencite{cavallo2017are}, which demonstrated the validity of using high-frequency online scraping to construct robust price indices (like our DSPI) that track real-time economic disparities better than traditional CPI baskets.

\subsection{Data Analysis}
The raw price data was processed in two stages. First, all local prices were converted to a common currency (USD) using market exchange rates (recorded in December 2024 and January 2025) to determine the "Nominal Price Inequality." Second, to assess "Real Affordability," these prices were calculated as a percentage of the \textit{Median National Monthly Wage} (sourced from OECD and World Bank data), providing a direct measure of the economic burden on the local consumer (`Price-to-Wage Ratio`). This approach replaces standard PPP adjustment to better reflect the specific affordability of subscription goods relative to disposable income.

It is important to note that a DSPI of 1.0 (Nominal Parity) does not imply equal affordability. Due to vast differences in median wages (e.g., Switzerland vs. India), a service priced identically in USD would be significantly more expensive for the Indian consumer in real terms (requiring a larger percentage of their income). Thus, the arbitrage incentive persists even at nominal parity if the local price is structured to be affordable for the local median earner.

The DSPI was calculated as the ratio of the local price to the US baseline price. A DSPI of 1.0 indicates price parity; a DSPI < 1.0 indicates a cheaper market (potential arbitrage source), and a DSPI > 1.0 indicates a more expensive market. Statistical variance analysis was performed to identify which service categories exhibit the highest degree of price discrimination.

\section{Phase 2: Qualitative Data Collection \& Analysis (for RQ2)}

\subsection{Coding Procedure}
The analysis follows a systematic coding approach inspired by the \textbf{Gioia Methodology} \parencite{gioia2013seeking}. This involves structuring data into 1st-order concepts (raw terms found in text), 2nd-order themes (theoretical categories like "Technical Blocking"), and aggregate dimensions (Strategic Responses).
While initially conceptualized for manual coding \parencite{duriau2007content}, this hierarchical structure provided the logic for the automated classification pipeline described below.

\input{methodology_details}

\subsection{Standard Qualitative Coding}
In addition to the automated pipeline, manual qualitative coding is applied to a sub-sample to capture themes that escape rigid categorization, such as the specific "tone" of VPN provider marketing (e.g., empowering vs. technical).

\section{Data Analysis Procedures}
\label{sec:analysis_procedures}

The final analytical step involved synthesizing the quantitative and qualitative data streams. 

\subsection{Statistical Analysis of the DSPI}
The pricing data was analyzed using Python. We calculated descriptive statistics (mean, median, standard deviation) for the DSPI. We also generated correlation matrices to find the link between a country's income and the subscription price, testing if price discrimination depends strictly on national wealth.

\subsection{Interpretation of Qualitative Classifications}
For the qualitative data, the JSON outputs from the Gemini 3 Flash pipeline were parsed and aggregated. The frequency of each "Strategic Frame" (e.g., \textit{Legal Compliance} vs. \textit{User Freedom}) and "Firm Action" (e.g., \textit{Technical Blocking}) was calculated per company and per year. 

To visualize the evolution of enforcement strategies, these frequencies were normalized against the total number of sentences per year to account for the growing length of ToS documents. This allowed for the generation of longitudinal trend lines (see Chapter 4). Finally, a comparative analysis was conducted to contrast the rhetoric of "Fortress" strategy firms (high blocking) against "Globalist" strategy firms (price harmonization), identifying the key markers of each business model archetype.
