This chapter presents the findings of the research objectively, without interpretation.
\label{chap:results}

\section{The Landscape of International Pricing: Findings from the DSPI}
\input{results_analysis}

\section{Strategic Framing by Digital Service Providers}
The qualitative analysis highlights a distinct "Coercive" framing strategy employed by digital service providers. The dominant rhetorical frame, appearing in over \textbf{65\%} of non-boilerplate sentences, is \textbf{Legal Compliance}. Firms consistently position their geographic restrictions not as business decisions, but as external mandates using language like "compliance with local laws," "licensing restrictions," and "obligations to content owners."

This framing serves a dual purpose: legimitization and blame-shifting. By externalizing the source of the restriction, firms attempt to deflect consumer frustration away from their pricing strategy and towards abstract legal entities. A secondary, though less frequent, frame is \textbf{Partner Protection}, appearing in 12\% of cases, where the firm positions itself as a steward of the creative ecosystem, arguing that geo-blocking is necessary to ensure artists are paid fairly. Marketing blogs and consumer-facing FAQs tend to soften this tone, focusing on "curating the best local experience," whereas the binding Terms of Service remain strictly litigious.

\section{Strategic Framing by VPN Providers}
In sharp contrast to the service providers, VPN companies adopt a "Liberation" and "Privacy" frame. The analysis of marketing materials from providers like NordVPN and ExpressVPN reveals a consistent narrative that reframes circumvention as \textbf{User Freedom}. The most common keywords include "unrestricted access," "freedom," and "bypass censorship," often conflating the evasion of commercial geo-blocks with the evasion of political censorship.

A secondary dominant frame is \textbf{Privacy/Security}. While many users purchase VPNs for streaming arbitrage, providers legitimize the service by emphasizing "military-grade encryption" and "anonymity." This allows users to adopt a "Privacy" neutralization technique—justifying their purchase as a security measure, with cheaper Netflix access being merely a fortunate side effect. The tone is consistently empowering, portraying the user as a savvy "digital citizen" reclaiming their rights against corporate overreach.
